The Rockerverse: Images, Packages, and Applications for Containerization with R

### 2020-01-27 manuscript.Rmd
add preprint template

>>>>

```{r preprint_pdf, eval=FALSE, include=FALSE}
# run this chunk, get the PDF, then revert changes in touched files
library("rmarkdown")
library("rticles")
unlink('manuscript_cache', recursive = TRUE)

# function is a copy of rticles::rjournal_article() but...
# - using RJWrapper_preprint_template.tex (which includes header.tex commands)
# - directly referencing unexported functions from rticles
# - direclty setting the keep_tex option
rjournal_style_preprint <- function (..., citation_package = "natbib") {
    rmarkdown::pandoc_available("2.2", TRUE)
    base <- rticles:::pdf_document_format("rjournal_article", highlight = NULL, 
        citation_package = citation_package, ...)
    base$pandoc$to <- "latex"
    base$pandoc$ext <- ".tex"
    base$pandoc$keep_tex <- TRUE # added
    base$post_processor <- function(metadata, utf8_input, output_file, 
        clean, verbose) {
      filename <- basename(output_file)
      if (filename != (filename2 <- gsub("_", "-", filename))) {
          file.rename(filename, filename2)
          filename <- filename2
      }
      m <- list(filename = xfun::sans_ext(filename))
      h <- rticles:::get_list_element(metadata, c("output", "rticles::rjournal_article", 
          "includes", "in_header"))
      h <- c(h, if (length(preamble <- unlist(metadata[c("preamble", 
          "header-includes")]))) {
          f <- tempfile(fileext = ".tex")
          on.exit(unlink(f), add = TRUE)
          xfun::write_utf8(preamble, f)
          f
      })
      #t <- find_resource("rjournal_article", "RJwrapper.tex")
      t <- here::here("RJwrapper_preprint_template.tex")
      rticles:::template_pandoc(m, t, "RJwrapper.tex", h, verbose)
      tinytex::latexmk("RJwrapper.tex", base$pandoc$latex_engine, 
          clean = clean)
    }
    base$knitr$opts_chunk$comment <- "#>"
    hilight_source <- rticles:::knitr_fun("hilight_source")
    hook_chunk = function(x, options) {
        if (rticles:::output_asis(x, options)) 
            return(x)
        paste0("```{=latex}\n\\begin{Schunk}\n", x, "\\end{Schunk}\n```")
    }
    hook_input <- function(x, options) paste(c("\\begin{Sinput}", 
        hilight_source(x, "sweave", options), "\\end{Sinput}", 
        ""), collapse = "\n")
    hook_output <- function(x, options) paste("\\begin{Soutput}\n", 
        x, "\\end{Soutput}\n", sep = "")
    base$knitr$knit_hooks <- rticles:::merge_list(base$knitr$knit_hooks, 
        list(chunk = hook_chunk, source = hook_input, output = hook_output, 
            message = hook_output, warning = hook_output, plot = knitr::hook_plot_tex))
    base
}

rmarkdown::render("manuscript.Rmd", output_format = rjournal_style_preprint())
```
